### 2020-06-18 manuscript/manuscript.rmd
update figure in page 3

x1= factor(taxon_rectangles$matrix, levels=c("Dunn2008", "Hejnol2009", "Philippe2009", "Nosenko2013_ribo_14615", "Ryan2013_est", "Moroz2014_3d", "Whelan2015_D20", "Borowiec2015_Total1080" , "Chang2015", "Whelan2017_full", "Simion2017"))

ggplot(data=taxon_rectangles) +
	scale_x_continuous(name="Gene sampling") +
	scale_y_continuous(name="Taxa sampling") +
	geom_rect( mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=clade )) +
	#scale_fill_manual(guide = guide_legend(reverse=TRUE))+
 scale_fill_manual(values = clade_colors, guide = guide_legend(reverse=TRUE))+
	#scale_fill_discrete(guide = guide_legend(reverse=TRUE, legend = "bottom right")) +
	facet_wrap( ~ matrix )

>>>>

taxon_rectangles$matrix= factor(taxon_rectangles$matrix, levels=c("Dunn2008", "Hejnol2009", "Philippe2009", "Nosenko2013_ribo_14615", "Ryan2013_est", "Moroz2014_3d", "Whelan2015_D20", "Borowiec2015_Total1080" , "Chang2015", "Whelan2017_full", "Simion2017"))

ggplot(data=taxon_rectangles) +
	scale_x_continuous(name="Gene sampling") +
	scale_y_continuous(name="Taxa sampling") +
	geom_rect( mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=clade )) +
	#scale_fill_manual(guide = guide_legend(reverse=TRUE))+
 scale_fill_manual(values = clade_colors, guide = guide_legend(reverse=TRUE))+
	#scale_fill_discrete(guide = guide_legend(reverse=TRUE, legend = "bottom right")) +
	facet_wrap( ~ matrix ) + theme_classic()
